Hidden Talents Multiverse Analysis

### 2021-06-28 manuscript/manuscript.Rmd
fix links and figure placement

---
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: false
    number_sections: false
    keep_tex: true
    extra_dependencies: ["booktabs","caption","longtable","float"]
geometry: margin=1in
mainfont: Times
fontsize: 11pt
endnote: no
header-includes:
- \usepackage{siunitx}
- \usepackage[utf8]{inputenc}
- \usepackage[english]{babel}
- \setlength{\parindent}{2em}
- \setlength{\parskip}{0em}
- \linespread{1.5}
- \usepackage{titlesec}
- \titleformat{\section}[block]{\normalsize\bfseries\filcenter}{}{1em}{}
- \titleformat{\subsubsection}[block]{\bfseries\itshape}{}{1em}{}
- \usepackage{indentfirst}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhf{}
- \fancyhead[R]{\thepage}
- \fancyhead[L]{HIDDEN TALENTS IN CONTEXT}
- \renewcommand\headrulewidth{0pt}
- \usepackage{fixltx2e}
- \usepackage{caption}
- \captionsetup[table]{labelfont={bf},labelformat={default}, labelsep={newline}}
- \captionsetup[figure]{labelfont={bf},labelformat={default}, labelsep={period}}
bibliography: references.bib
csl: nature.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  fig.align = "center",
  fig.pos = "H",  
  fig.show = "asis",
  message = FALSE,
  warning = FALSE
)

@@

Before conducting analyses, we identified six arbitrary data processing decisions each with two alternatives (see Arbitrary Decisions section). These criteria were 1) including the after-school club sample or not; 2) including participants with minor distractions during testing or not; 3) including participants who missed one trap question or not (those who missed more than 1 were already excluded); 4) including participants receiving special education (participants receiving more \> 60 minutes/day were already excluded) or not; 5) including participants who performed at or below chance levels of accuracy on the attention-shifting task or not (see <https://osf.io/kvt5e/> for more information); and 6) residualizing social desirability scores out of adversity scores or not. Using all possible combinations of arbitrary decisions, we constructed a multiverse of `r length(multi_data_list)` datasets. The minimum and maximum sample sizes were `r map_dbl(multi_data_list, "n") %>% min()` and `r map_dbl(multi_data_list, "n") %>% max()`, respectively.

@@

Figures \@ref(fig:figure2) and \@ref(fig:figure3) visualize multiverse task version × adversity interaction results for attention shifting and working memory performance, including depictions of performance on abstract and ecological task versions across high ($+$1 *SD*) and low ($-$ *SD*) adversity exposure (Figures \@ref(fig:figure2)a and \@ref(fig:figure3)a), p-curves associated with each interaction term (Figures \@ref(fig:figure2)b and \@ref(fig:figure3)b), sorted interaction -coefficients across arbitrary decisions (Figures \@ref(fig:figure2)c and \@ref(fig:figure3)c), sample sizes (Figures \@ref(fig:figure2)d and \@ref(fig:figure3)d), and a specification grid showing the arbitrary data processing decisions associated with each effect (Figures \@ref(fig:figure2)e and \@ref(fig:figure3)e).

We preregistered all primary analyses on the Open Science Framework (OSF; <https://osf.io/6r95z/>), including an updated primary analysis plan (<https://osf.io/4vsnz/>), which included more details. We conducted secondary analyses after our primary analyses (see Secondary Analyses below). Before conducting these analyses, we uploaded secondary analysis plans (see <https://osf.io/7fu35/> and <https://osf.io/wcauf/>), explaining the goals and purpose of each secondary analysis. A Red Team Critic[@market] successfully reproduced (<https://github.com/ethan-young/hidden-talents-multiverse/pull/1/>) and verified (REPORT XXX) all analyses prior to submission.

@@

@@

We followed-up our primary analyses with two sets of secondary, exploratory analyses. We uploaded secondary analysis plans to the OSF prior to conducting them (see <https://osf.io/7fu35//> and <https://osf.io/wcauf//>). These analyses focused on two questions. First, in contrast to prior work[@mittal2015; @young2018], we found limited support for improved working memory updating performance in relation to unpredictability (although we found a main effect of unpredictability on attention shifting). However, prior work measured retrospective perceptions of unpredictability whereas the current combined perceptions with more objective, interview-based measures. Thus, one possibility is that specific components of our composite adversity measures (unpredictability, violence exposure, and poverty exposure) have unique associations with attention shifting and working memory updating performance. To address this, we expanded our multiverse approach to include each component of our predictor variables as additional arbitrary decisions.

@@

To calculate attention-shifting scores, we first cleaned trial-level data [@friedman2008; @miyake2000]. We removed fast and slow reaction times and removed trials after incorrect responses (see <https://osf.io/74xjy/> for details). We then subtracted the average reaction time on valid switch trials from the average reaction time on valid repeat trials to calculate switch cost scores. The switch cost measures the relative delay in reaction time caused by switching between categorization rules. Average switch costs on the standard and ecological versions were `r txt2_dvs$abs_shifting_sc$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_sc$sd` *ms*) and `r txt2_dvs$eco_shifting_sc$mean` ms (*SD* = `r txt2_dvs$eco_shifting_sc$sd` ms), respectively (*r* = `r txt5_cor$shifting$r`, *n* = `r txt5_cor$shifting$n`). Higher switch costs mean longer reaction times on switch trials compared to repeat trials. Larger switch costs indicate less efficient attention shifting.

@@

We identified six arbitrary data processing decisions. First, we conducted analyses with and without the after-school club sample. We did this because our procedure was slightly different across the two samples and the testing environment was more disruptive in the clubs compared with the middle school. Second, we conducted analyses with and without participants with minor distractions during testing. Third, we analyzed the data with and without participants who missed one trap question (those who missed more than 1 were already excluded). Fourth, we analyzed data with and without participants having any amount of special education (participants receiving more \> 60 minutes were already excluded). Fifth, we analyzed data with and without participants who performed at or below chance levels of accuracy on the attention-shifting task (see <https://osf.io/kvt5e/> for more information).

>>>>

---
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: false
    number_sections: false
    keep_tex: true
    extra_dependencies: ["booktabs","caption","longtable","float"]
geometry: margin=1in
mainfont: Times
fontsize: 11pt
endnote: no
urlcolor: blue
header-includes:
- \usepackage{siunitx}
- \usepackage[utf8]{inputenc}
- \usepackage[english]{babel}
- \setlength{\parindent}{2em}
- \setlength{\parskip}{0em}
- \linespread{1.5}
- \usepackage{titlesec}
- \titleformat{\section}[block]{\normalsize\bfseries\filcenter}{}{1em}{}
- \titleformat{\subsubsection}[block]{\bfseries\itshape}{}{1em}{}
- \usepackage{indentfirst}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhf{}
- \fancyhead[R]{\thepage}
- \fancyhead[L]{HIDDEN TALENTS IN CONTEXT}
- \renewcommand\headrulewidth{0pt}
- \usepackage{fixltx2e}
- \usepackage{caption}
- \captionsetup[table]{labelfont={bf},labelformat={default}, labelsep={newline}}
- \captionsetup[figure]{labelfont={bf},labelformat={default}, labelsep={period}}
bibliography: references.bib
csl: nature.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  fig.align = "center",
  fig.pos = "!",  
  fig.show = "asis",
  message = FALSE,
  warning = FALSE
)

@@

Before conducting analyses, we identified six arbitrary data processing decisions each with two alternatives (see Arbitrary Decisions section). These criteria were 1) including the after-school club sample or not; 2) including participants with minor distractions during testing or not; 3) including participants who missed one trap question or not (those who missed more than 1 were already excluded); 4) including participants receiving special education (participants receiving more \> 60 minutes/day were already excluded) or not; 5) including participants who performed at or below chance levels of accuracy on the attention-shifting task or not (see [attention shifting data cleaning procedure]( https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for more information); and 6) residualizing social desirability scores out of adversity scores or not. Using all possible combinations of arbitrary decisions, we constructed a multiverse of `r length(multi_data_list)` datasets. The minimum and maximum sample sizes were `r map_dbl(multi_data_list, "n") %>% min()` and `r map_dbl(multi_data_list, "n") %>% max()`, respectively.

@@

Figures \@ref(fig:figure2) and \@ref(fig:figure3) visualize multiverse task version × adversity interaction results for attention shifting and working memory performance, including depictions of performance on abstract and ecological task versions across high ($+$ 1 *SD*) and low ($-$ 1 *SD*) adversity exposure (Figures \@ref(fig:figure2)a and \@ref(fig:figure3)a), p-curves associated with each interaction term (Figures \@ref(fig:figure2)b and \@ref(fig:figure3)b), sorted interaction -coefficients across arbitrary decisions (Figures \@ref(fig:figure2)c and \@ref(fig:figure3)c), sample sizes (Figures \@ref(fig:figure2)d and \@ref(fig:figure3)d), and a specification grid showing the arbitrary data processing decisions associated with each effect (Figures \@ref(fig:figure2)e and \@ref(fig:figure3)e).

We preregistered all primary analyses on the Open Science Framework (OSF; see the [osf project link](https://osf.io/6r95z/?view_only=92d55bd3b9834468acd3a7cef5c3febd), including an [updated primary analysis plan](https://osf.io/4vsnz/?view_only=92d55bd3b9834468acd3a7cef5c3febd), which included more details. We conducted secondary analyses after our primary analyses (see Secondary Analyses below). Before conducting these analyses, we uploaded secondary analysis plans (see the [first secondary analysis plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [second plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd), explaining the goals and purpose of each secondary analysis. A Red Team Critic[@market] successfully reproduced and verified (REPORT XXX) all analyses prior to submission.

@@

We followed-up our primary analyses with two sets of secondary, exploratory analyses. We uploaded secondary analysis plans to the OSF prior to conducting them (see the [first secondary analysis plan](https://osf.io/7fu35/?view_only=92d55bd3b9834468acd3a7cef5c3febd) and the [second plan](https://osf.io/wcauf/?view_only=92d55bd3b9834468acd3a7cef5c3febd)). These analyses focused on two questions. First, in contrast to prior work[@mittal2015; @young2018], we found limited support for improved working memory updating performance in relation to unpredictability (although we found a main effect of unpredictability on attention shifting). However, prior work measured retrospective perceptions of unpredictability whereas the current combined perceptions with more objective, interview-based measures. Thus, one possibility is that specific components of our composite adversity measures (unpredictability, violence exposure, and poverty exposure) have unique associations with attention shifting and working memory updating performance. To address this, we expanded our multiverse approach to include each component of our predictor variables as additional arbitrary decisions.

@@

@@

To calculate attention-shifting scores, we first cleaned trial-level data [@friedman2008; @miyake2000]. We removed fast and slow reaction times and removed trials after incorrect responses (see [attention shifting data cleaning procedure]( https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for details). We then subtracted the average reaction time on valid switch trials from the average reaction time on valid repeat trials to calculate switch cost scores. The switch cost measures the relative delay in reaction time caused by switching between categorization rules. Average switch costs on the standard and ecological versions were `r txt2_dvs$abs_shifting_sc$mean` *ms* (*SD* = `r txt2_dvs$abs_shifting_sc$sd` *ms*) and `r txt2_dvs$eco_shifting_sc$mean` ms (*SD* = `r txt2_dvs$eco_shifting_sc$sd` ms), respectively (*r* = `r txt5_cor$shifting$r`, *n* = `r txt5_cor$shifting$n`). Higher switch costs mean longer reaction times on switch trials compared to repeat trials. Larger switch costs indicate less efficient attention shifting.

@@

We identified six arbitrary data processing decisions. First, we conducted analyses with and without the after-school club sample. We did this because our procedure was slightly different across the two samples and the testing environment was more disruptive in the clubs compared with the middle school. Second, we conducted analyses with and without participants with minor distractions during testing. Third, we analyzed the data with and without participants who missed one trap question (those who missed more than 1 were already excluded). Fourth, we analyzed data with and without participants having any amount of special education (participants receiving more \> 60 minutes were already excluded). Fifth, we analyzed data with and without participants who performed at or below chance levels of accuracy on the attention-shifting task (see [attention shifting data cleaning procedure]( https://osf.io/kvt5e/?view_only=92d55bd3b9834468acd3a7cef5c3febd) for more information).
